Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
State again, that Haddock is the standard way to document Haskell code
describing reusable spec.

Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt containers} package.

@@

\begin{itemize}
\item Some type classes have their laws.
\item We can use Hspec to enforce such properties.
\item If such properties are reusable among instances,
we can avoid boilerplates.
\item reusable spec can do this.
\end{itemize}

@@

\noindent The following is an example to apply this laws
to lists.

@@

\begin{itemize}
\item we should prepare this kind of laws.
\end{itemize}

>>>>

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt containers} package.

@@

Reusable spec is an idea to scrap boilerplate of evidence.
For instance, without reusable spec,
each developer of an instance of a type class should
express evidence for its laws.
Since instances of a type class share API,
we can avoid such boilerplate.
The following is an example to implement
evidence for Monoid laws:

@@

\noindent This can be used for any instances of Monoid.
Here is an example to apply it to a list:

@@

\noindent We have already implemented this experimentally.
We should ensure the practicality of reusable spec and
prepare reusable spec to cover variety of type classes.
